---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---
#Lab 2
#group activity
###2/1/2018


[x] question 1

 How are ratings distributed? 
 
 Draw a histogram of ratings and describe it.

```{r echo=FALSE}
library(ggplot2)
choco <- read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")


ggplot(choco, aes(x = Rating)) +    geom_histogram(binwidth = .25) 


```
 
 
 Notice that ratings 5 and 1 are distant, thus the can be classified as outliers.


[x] question 2

 -Do ratings depend on the cocoa percentage of a chocolate bar?
 
There is not enough evidence to determine if rating is directly proportional to percentage of a chocolate bar. 


```{r echo=FALSE}
library(ggplot2)
choco <- read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")


ggplot(data = choco , aes (x= Cocoa.Pct, y= Rating)) + geom_point() 
ggplot(data = choco , aes (x= Cocoa.Pct, y= Rating)) + geom_line() 


```

[x] question 3

 -How do ratings compare across different company locations? Focus on the three locations with the most ratings:
 


First, show the locations with most ratings

```{r echo=FALSE}
library(ggplot2)

comp <- dplyr::filter(choco, Company.Location %in% c("U.S.A.", "France", "Canada"))

ggplot(data = comp , aes (x= Company.Location, y= Rating)) + geom_point()
 
```

Now we compare across different company locations using boxplots


```{r echo=FALSE}
library(ggplot2)
choco <- read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")


comp <- dplyr::filter(choco, Company.Location %in% c("U.S.A.", "France", "Canada"))


ggplot(data = comp, aes(y = Rating, x  = Company.Location)) + geom_boxplot() 

```



From the box plot we can conclude the following: 

* Median seems to be the same for all locations

* Canada : seems to have greater amount of points in the upper section (median-upper quartile) 

* France : seems to have roughly the same amount of points between median-upper quartile and median-lower quartile

* USA		: seems to have greater amount of points in the lower section (median-lower quartile)

* we can also see outliers for France and the US 

It can be said that Canada is the location with highest rating average, followed by France and the US.

